---
title: "README"
author: "Bill Su"
date: "June 16, 2015"
output: html_document
---
##Introduction

The propose of this document is to present the code in the directory and how it works. For this project, we are tasked to accomplish five objectives. 

1.Merges the training and the test sets to create one data set.
2.Extracts only the measurements on the mean and standard deviation for each measurement. 
3.Uses descriptive activity names to name the activities in the data set
4.Appropriately labels the data set with descriptive variable names. 
5.From the data set in step 4, creates a second, independent tidy data set with the average of each variable for each activity and each subject.

I will list the code below and explain which task the code has accomplished. 

##The first step was to load all the datasets. 
```{r}

library(dplyr)

##Reading of Data
subjet_test <- read.table("subject_test.txt")
subjet_train <- read.table("subject_train.txt")
X_test <- read.table("X_test.txt")
X_train <- read.table("X_train.txt")
y_test <- read.table("y-test.txt")
y_train <- read.table("y-train.txt")
features <- read.table("features.txt")

```
##Then I have assigned proper heading to all variables and merged the data, completed task #1 and #4
```{r}

##Making sure the labels are correct
labels <- features$V2
colnames(subject_test) <- c("subject")
colnames(subject_train) <- c("subject")
colnames(y_test) <- c("activity")
colnames(y_train) <- c("activity")
colnames(X_test) <- labels
colnames(X_train) <- labels

##Combine multiple dataframes into one
test <- cbind(subject_test, X_test, y_test)
train <- cbind(subject_train, X_train, y_train)
data <- rbind (test, train)
```

##Then I have extracted only necessary information from the dataset, therefore completed task NO. 2

```{r}
##Tidy up the dataset
selected <- data[, grepl("std()", colnames(data)) | 
                         grepl("mean()", colnames(data)) ]
activity <- data$activity
subject <- data$subject
tidy <- cbind(activity, subject, selected)
```

##Then I have created a new column activity_name in which the name of the activites are displayed correctly and descriptivly. Completing task #3

```{r}

## Making activities real names
tidy$activity_name[tidy$activity == 1] <- "WALKING"
tidy$activity_name[tidy$activity == 2] <- "WALKING_UPSTAIRS"
tidy$activity_name[tidy$activity == 3] <- "WALKING_DOWNSTAIRS"
tidy$activity_name[tidy$activity == 4] <- "SITTING"
tidy$activity_name[tidy$activity == 5] <- "STANDING"
tidy$activity_name[tidy$activity == 6] <- "LAYING"
tidy <- tidy[,c(ncol(tidy),1:(ncol(tidy)-1))]

```

##Finally, after everything is set, I have compeleted step 5 with the following code. 

```{r}
##Creating and outputing the new data
NewData<-aggregate(. ~subject + activity_name, tidy, mean)
write.table(NewData, output.txt, row.name=FALSE) 
```

##For code book for the output data, please view the codebook.txt document in the same repository. Thank you for reading (or maybe you have to :D)

